log hyperparameter optimization

### 2020-04-01 simulation_study/hpoptimization/README.Rmd
test ini file

hpsets[condition[7:10], ,"all"] <- 1
```

@@

>>>>

hpsets[condition[7:10], ,"all"] <- 1

```

@@

--- 
# Visual inspection 30-03-2020

## classifiers
```{bash, eval = FALSE}
# script to show all lisa.err files to see if processes done yes/no
.catlisaerr.sh
```
- svm 
  - ace (3x) 3 times the time. 
  - nudging 7x
  - ptsd 7x 
  - software 3x (of 4)
  - virus 5x
  - wilson 3x
    - all 10x
- rf 
  - software 2x 
  - all 3x
- rest is fine, over 1000 runs and seems not to improve much. 
```{r}
hpsets[condition[c(1,4)], , c("one", "all")] <- 2
hpsets[condition[c(2,3)],  d[c(1:2, 5:6)], "one"] <- 2
```

Sent in around 13 pm (30.03.2020)
```{r}
# svm extra time 
cons <- expand.grid(c = classifier[3], stringsAsFactors = FALSE, d= d)
cons$t <- c("36", rep("84", 2), "48", "60", "36")
extrasvm1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
names(extrasvm1) <- c("7867379","7867380", "7867382", "7867383", "7867384", "7867387")

cons <- expand.grid(c=classifier[2], stringsAsFactors = FALSE, d=d[3:4])

cons$t <- c("06", "24")

extrarf1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
names(extrarf1) <- c("7867388", "7867389")

# later check rf - ptsd - one
hpsets[condition[2], d[3], "one"] <- 2

cons <- data.frame(c = classifier[2:3], t = c("5-00", "5-00"))
extraall <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -r 23", cons$t, cons$c)
names(extraall) <- c("7867412", "7873506")

# save scripts for reproducibility 
write.table(c(extrasvm1, extrarf1), file = "scripts/one/extratime_classifier.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
write.table(extraall, file = "scripts/n/extratime_classifier.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
```

## doc2vec 
```{bash, eval = FALSE}
# bash script to print all hyperopt results. 
./show.sh
```

- nn-2-layer - try again with -r 11.  (for all datasets still doesn't work )

```{r}
# redo nn-2-layer with doc2vec. 
#./cart_hyper_run.py hyper-active -t 01:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 11 7867616 test for an hour 
hpsets[condition[10], , "one"] <- 8 # error
cons <- expand.grid(c = classifier[5], stringsAsFactors = FALSE, d=d)
cons$t <- "5-00:00:00"
nn2dv1 <- sprintf("./cart_hyper_run.py hyper-active -t %s -m %s -b double -e doc2vec -q max -d %s -r 11", cons$t, cons$c, cons$d)
write.table(nn2dv1, file = "scripts/one/nn2d2v.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(nn2dv1) <- c("7872280", "7872281", "7872282", "7872283", "7872284", "7872285")
hpsets[condition[10], , "one"] <- 1 # sent in again
# this can be turnt of afer 52 hours. (thursday morning) 02.04

nn2d2vall <- c("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m nn-2-layer -b double -e doc2vec -q max -r 4")
write.table(nn2d2vall, file = "scripts/n/nn2d2v.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(nn2d2vall) <- "7873511"
```

- rf is done 
  - ace 3x? 
  - nudging 2x 
  - ptsd 6x
  - software 10 x
  - virus 1.5 x 
  - wilson 1x

```{r}
# redo random forest d2v
t <- rep(c("36", "24", "72", "5-00", "18", "12"))
x_d2v_rf <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m rf -b double -e doc2vec -q max -d %s -r 23", t, d)
# one test of doc2vec 
write.table(x_d2v_rf, file = "scripts/one/x_d3v_rf.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(x_d2v_rf) <- c("7867607", "7867608", "7867609", "7867610", "7867611", "7867612")
```

# asreview create-config

# export config files 
(from all files in output :) )

```{r}
d4 <- c(paste(d[1:5], collapse=","), 
        paste(d[2:6], collapse=","), 
        paste(d[c(3:6,1)], collapse = ","), 
        paste(d[c(4:6, 1:2)], collapse=","),
        paste(d[c(5:6, 1:3)], collapse = ","),
        paste(d[c(6, 1:4)], collapse = ","))
cons <- expand.grid(c = classifier, d = d4, f=c("tfidf", "doc2vec"), stringsAsFactors = FALSE)
cons <- cons[!(cons$c == "nb" & cons$f == "doc2vec"), ]
cons$r <- ifelse(cons$c == "nn-2-layer", "11", "23")
cons$t <- ifelse(cons$c == "nb", "12", "5-00")
# all models
n_1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e %s -q max -d %s -r %s", cons$t, cons$c, cons$f, cons$d, cons$r)
write.table(n_1, file = "scripts/n-1/all_models.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)

# job names
names(n_1) <- c("7873344", "7873345", "7873346", "7873347", "7873348",
                "7873360", "7873361", "7873363", "7873364", "7873365",
                "7873378", "7873379", "7873381", "7873382", "7873383",
                "7873392", "7873393", "7873394", "7873396",
                "7873396",
                "7873397", "7873398", "7873399", "7873400", "7873401",
                "7873407", "7873408", "7873409", "7873411", "7873413",
                "7873425", "7873427", "7873429", "7873431", "7873433",
                "7873446", "7873448", "7873450", "7873453", 
                "7873455",
                "7873460", "7873461", "7873462", "7873463",
                "7873464",
                "7873466", "7873467", "7873468", "7873469", "7873470", 
                "7873471", "7873472", "7873473", "7873474")

hpsets[c(1:5, 6:10),,"four"] <- 1
```

31.03.2020
### all 
all SCDD, LCDD RCDD, resend for 5 days 
```{r}
# more time for doc2vec all datasets - svm + logistic 
d2vall
cons <- expand.grid(c = classifier[2:4], stringsAsFactors = FALSE)
d2vall_x <- sprintf("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m %s -b double -e doc2vec -q max -r 23", cons$c)
write.table(d2vall_x, file = "scripts/n/d2v_all_x.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(d2vall_x) <- c("7873497", "7873499","7873500")
```

try nn2 with tfidf -r 11

checkout nn 2 layer tfidf

### one
one LCDD, for 2x the time 
one SCDD for 1x the time 
```{r}
cons <- expand.grid(c = classifier[3:4], d = d, stringsAsFactors = FALSE)
cons$t <- ifelse(cons$c=="logistic", "96", "48")
d2v1_x <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", cons$t, cons$c, cons$d)
write.table(d2v1_x, file = "scripts/one/d2vone_x.txt", sep="\t", quote = FALSE, row.names = FALSE)

names(d2v1_x) <- c("7877706", "7877707", "7877708", "7877709", "7877710",
                   "7877711", "7877712", "7877713", "7877714", "7877715", "7877716", 
                   "7877717")
```

```{r}
hpsets[condition[2], d[4] , "one"] <- 2
```
